---
title: "process-FCM-data"
output: html_document
date: "2024-01-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Extract cell counts and other parameters from flow cytometry data

```{r dependencies}
pacman::p_load(flowCore,ggplot2,reshape2,dplyr,ggridges,data.table,patchwork)
```

## Reading in data

Plate wells file contains the correspondence between the FCM wells and the experiment samples.

```{r read_914, echo=FALSE}
setwd("/Users/akq/Documents/Graduate School/Papers/2024-N-Temp-Colim/nitrate-temp-colim/code")
well_spec = read.table("../data/914/fcm_914/well-data.tsv", row.names=NULL, header=TRUE)
well_spec$n_conc = as.character(well_spec$n_conc)
well_spec$strain = as.character(well_spec$strain)
well_spec_refeed = well_spec
top_level = "../data/914/fcm_914"
top_level_refeed = "../data/914/fcm_914/914_spike_fcm"
fcm_all = data.frame()
for (date in c("2023-10-12","2023-10-13","2023-10-14",
               "2023-10-15","2023-10-16","2023-10-17",
               "2023-10-18","2023-10-19","2023-10-20",
               "2023-10-21")) {
    refeed=FALSE
    if (date %in% c("2023-10-19")) {
        well_spec_refeed=data.frame("Well"=c("A10","A11","A12",
                                      "B10","B11","B12"),
                             "strain"=c("914","914","914","914","914","914"),
                             "n_conc"=c("Unamended-10%","Unamended-10%","Unamended-10%",
                                       "Spiked-100%","Spiked-100%","Spiked-100%"),
                             "temp_c"=c(18,18,18,18,18,18),
                             "rep"=c("A","B","C","A","B","C"))
        refeed=TRUE
    } else if (date %in% c("2023-10-21")) {
        
        well_spec_refeed=data.frame("Well"=c("C01","C02","C03",
                                      "D01","D02","D03","C04","C05","C06",
                                      "D04","D05","B06","C07","C08",
                                      "D07","D08"),
                             "strain"=c("914","914","914","914","914","914",
                                        "914","914","914","914","914","914",
                                        "914","914","914","914"),
                             "n_conc"=c("Unamended-10%","Unamended-10%","Unamended-10%",
                                       "Spiked-100%","Spiked-100%","Spiked-100%",
                                       "Unamended-10%","Unamended-10%","Unamended-10%",
                                       "Spiked-100%","Spiked-100%","Spiked-100%",
                                       "Unamended-10%","Unamended-10%",
                                       "Spiked-100%","Spiked-100%"),
                             "temp_c"=c(18,18,18,18,18,18,
                                      22,22,22,22,22,22,
                                      28,28,28,28),
                             "rep"=c("A","B","C","A","B","C",
                                     "A","B","C","A","B","C",
                                     "A","B","A","B"))
        refeed=TRUE
    } else if (date %in% c("2023-10-20")) {
        well_spec_refeed=data.frame("Well"=c("A01","A02","A03",
                                      "B01","B02","B03","A04","A05","A06",
                                      "B04","B05","B06","A07","A08",
                                      "B07","B08"),
                             "strain"=c("914","914","914","914","914","914",
                                        "914","914","914","914","914","914",
                                        "914","914","914","914"),
                             "n_conc"=c("Unamended-10%","Unamended-10%","Unamended-10%",
                                       "Spiked-100%","Spiked-100%","Spiked-100%",
                                       "Unamended-10%","Unamended-10%","Unamended-10%",
                                       "Spiked-100%","Spiked-100%","Spiked-100%",
                                       "Unamended-10%","Unamended-10%",
                                       "Spiked-100%","Spiked-100%"),
                             "temp_c"=c(18,18,18,18,18,18,
                                      22,22,22,22,22,22,
                                      28,28,28,28),
                             "rep"=c("A","B","C","A","B","C",
                                     "A","B","C","A","B","C",
                                     "A","B","A","B"))
        refeed=TRUE
    }
    if (!grepl("csv",date) & !grepl("ipynb",date) & !grepl("maintenance",date)) {
        fcs_dir = file.path(top_level,date)
        for (curr_well in list.files(fcs_dir)) {
            curr_well_name = unlist(strsplit(curr_well, "\\."))[1]
            if (length(which(grepl(curr_well_name, well_spec$Well))) > 0) {
                fcm = read.FCS(file.path(fcs_dir,curr_well),emptyValue = FALSE,
                       alter.names=TRUE)
                total_time = difftime(as.POSIXct(as.character(fcm@description["$ETIM"]),
                                                 format="%H:%M:%OS"),
                                      as.POSIXct(as.character(fcm@description["$BTIM"]),
                                                 format="%H:%M:%OS"),
                                      units="mins")
                fcm_df = as.data.frame(exprs(fcm))
                fcm_df$Date = date
                fcm_df$Well = curr_well_name
                fcm_df$Time = total_time
                fcm_df = fcm_df %>% dplyr::left_join(well_spec, by= "Well")
                fcm_all = fcm_all %>% bind_rows(fcm_df %>% dplyr::mutate(Time=as.numeric(Time)))
            }
        }
        
        if (refeed) {
          fcs_dir = file.path(top_level_refeed,date)
          for (curr_well in list.files(fcs_dir)) {
            curr_well_name = unlist(strsplit(curr_well, "\\."))[1]
            if (length(which(grepl(curr_well_name, well_spec_refeed$Well))) > 0) {
              fcm = read.FCS(file.path(fcs_dir,curr_well),emptyValue = FALSE,
                     alter.names=TRUE)
              total_time = difftime(as.POSIXct(as.character(fcm@description["$ETIM"]),
                                               format="%H:%M:%OS"),
                                    as.POSIXct(as.character(fcm@description["$BTIM"]),
                                               format="%H:%M:%OS"),
                                    units="mins")
              fcm_df = as.data.frame(exprs(fcm))
              fcm_df$Date = date
              fcm_df$Well = curr_well_name
              fcm_df$Time = total_time
              fcm_df = fcm_df %>% dplyr::left_join(well_spec_refeed, by= "Well")
              fcm_all = fcm_all %>% bind_rows(fcm_df %>% dplyr::mutate(Time=as.numeric(Time)))
            }
          }
        }
    }
}
```

Write out the concentration data for us to use in the ROS script.

```{r write_out_conc}

conc_cell=fcm_all %>%
    dplyr::mutate(logFSC = log10(FSC.H), logFL3 = log10(FL3.H)) %>%
    dplyr::filter((logFSC > 4) & (logFL3 > 5.5)) %>%
    dplyr::group_by(Time, Date, Well, strain, n_conc, temp_c, rep) %>%
    dplyr::tally() %>%
    dplyr::mutate(ConcCellmL = n / 35 / as.numeric(Time) * 10^3 / 1)

write.csv(conc_cell,"../data/914/914_all_conc.csv")
```



```{r read_874, echo=FALSE}
setwd("/Users/akq/Documents/Graduate School/Papers/2024-N-Temp-Colim/nitrate-temp-colim/code")
well_spec = read.table("../data/874/fcm_874/well-data.tsv", row.names=NULL, header=TRUE)
top_level = "../data/914/fcm_874"
fcm_all = data.frame()
for (date in c("2023-10-12","2023-10-13","2023-10-14",
               "2023-10-15","2023-10-16","2023-10-17",
               "2023-10-18","2023-10-19","2023-10-20",
               "2023-10-21")) {
    if (!grepl("csv",date) & !grepl("ipynb",date) & !grepl("maintenance",date)) {
        fcs_dir = file.path(top_level,date)
        for (curr_well in list.files(fcs_dir)) {
            curr_well_name = unlist(strsplit(curr_well, "\\."))[1]
            if (length(which(grepl(curr_well_name, well_spec$Well))) > 0) {
                fcm = read.FCS(file.path(fcs_dir,curr_well),emptyValue = FALSE,
                       alter.names=TRUE)
                total_time = difftime(as.POSIXct(as.character(fcm@description["$ETIM"]),
                                                 format="%H:%M:%OS"),
                                      as.POSIXct(as.character(fcm@description["$BTIM"]),
                                                 format="%H:%M:%OS"),
                                      units="mins")
                fcm_df = as.data.frame(exprs(fcm))
                fcm_df$Date = date
                fcm_df$Well = curr_well_name
                fcm_df$Time = total_time
                fcm_df = fcm_df %>% dplyr::left_join(well_spec, by= "Well")
                fcm_all = fcm_all %>% bind_rows(fcm_df %>% dplyr::mutate(Time=as.numeric(Time)))
            }
        }
    }
}
```

Now that we have all the FCM data read in, we can get our cell concentrations and read those out for normalizing the ROS data.

```{r plot_conc}
conc_cell=fcm_all %>%
    dplyr::mutate(logFSC = log10(FSC.H), logFL3 = log10(FL3.H)) %>%
    dplyr::filter((logFSC > 4) & (logFL3 > 5.5)) %>%
    dplyr::group_by(Time, Date, Well, strain, n_conc, temp_c, rep) %>%
    dplyr::tally() %>%
    dplyr::mutate(ConcCellmL = n / 35 / as.numeric(Time) * 10^3 / 1)

ggplot(conc_cell) +
    geom_point(aes(x = as.Date(Date,format="%Y-%m-%d"), 
                   fill = factor(n_conc), y=ConcCellmL),pch=21)+
    geom_line(aes(x = as.Date(Date,format="%Y-%m-%d"), 
                  y = ConcCellmL, col = factor(n_conc), 
                  group=paste0(n_conc,temp_c,strain,rep))) +
    theme_bw(base_size=10) + ylab("Concentration (cell/mL)") + xlab("Date") + 
    facet_wrap(~temp_c,nrow=2)
```

```{r size}
ggplot(fcm_all %>% 
       dplyr::mutate(logFSC = log10(FSC.H), logFL3 = log10(FL3.H)) %>%
       dplyr::filter((logFSC > 4) & (logFL3 > 5.5)) %>%
       dplyr::group_by(Date,strain,n_conc,temp_c,Well) %>% 
       dplyr::summarize(meanFSC=mean(log10(FSC.H))) %>%
       dplyr::left_join(conc_cell)) +
    geom_point(aes(x = as.Date(Date,format="%Y-%m-%d"), 
                   y = meanFSC, fill = factor(n_conc), size=ConcCellmL),pch=21)+
    geom_line(aes(x = as.Date(Date,format="%Y-%m-%d"), 
                   y = meanFSC, col = factor(n_conc), group=paste0(n_conc,temp_c,strain,rep))) + ylim(c(5.7,6.4)) + theme_bw(base_size=12) + ylab("cell size proxy") + xlab("Date")
```

